Named Entity Recognition for Web Data Extraction

### 2019-05-18 tex/article.tex
NLE article.

% \documentclass[sigconf]{acmart}
% \settopmatter{printacmref=false} % Removes citation information below abstract
% \renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
% \pagestyle{plain} % removes running headers
% \setcopyright{none}

\usepackage{booktabs} % For formal tables
\usepackage[ruled]{algorithm2e} % For algorithms
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{amsfonts}
\usepackage{multirow}

@@

@@

\title{Web data extraction through named entity labeling}

\author{João Mateus de Freitas Veneroso}
% \affiliation{%
%   \institution{Universidade Federal de Minas Gerais}
%   \streetaddress{Av. Pres. Antônio Carlos, 6627 - Pampulha}
%   \city{Belo Horizonte}
%   \state{MG}
%   \postcode{31270-901}
%   \country{Brazil}}
% \email{jmfveneroso@gmail.com}
% 
% \author{Berthier Ribeiro-Neto}
% \affiliation{%
%   \institution{Universidade Federal de Minas Gerais}
%   \streetaddress{Av. Pres. Antônio Carlos, 6627 - Pampulha}
%   \city{Belo Horizonte}
%   \state{MG}
%   \postcode{31270-901}
%   \country{Brazil}}
% \email{berthier@dcc.ufmg.br}
% \email{berthier@google.com}

@@

Web data extraction methods often rely on hand-coded rules to 
identify and extract data from web pages. These methods are usually
suited for extracting information from repeating templates inside
the same website, however they perform poorly on extraction 
tasks across different websites. Alternatively, statistical and 
machine-learning-based sequence labeling methods provide a more flexible 
approach to Web data extraction. HTML text is ocasionally very different 
from plain text because sentences can be too short to provide adequate 
context for conventional Named Entity Recognition methods to work 
properly. Also, the HTML structure can encode information that is not 
replicated in the text. Nonetheless, these limitations can be overcome by
adequate feature engineering, the use of pre-trained word 
embeddings and neural character representations. In this article, we 
evaluate the performance of different methods of named entity recognition 
on the task of Web data extraction. In particular, we introduce a novel 
dataset consisting of faculty listings from university webpages across
the world in multiple languages and test the NER models on the task of 
extracting researcher names from these listings. We found that a 
neural network architecture that combines a bidirectional LSTM with
a Conditional Random Fields output layer and LSTM-based character 
representations outperforms other methods on the researcher name 
extraction task, achieving an F1-score of 0.8867 with no feature engineering. 
With the addition of hand crafted features, the F1-score can be slightly 
improved to 0.8995 with another neural architecture that incorporates
CNN-based character representations.

@@

% \keywords{Named entity recognition, information extraction, web data extraction}

@@

Web data extraction (WDE) is the task of automatically extracting structured 
information from unstructured or semi-structured Web documents. The input 
usually consists of Web documents containing a number of predetermined entities 
organized in a similar manner. The web data extraction task consists of 
identifying these entities and organizing them according to a template.

HTML documents most often lie in between the structured/unstructured 
data paradigm. DOM hierarchy, element disposition, CSS classes, and other 
features related to the document structure and indirectly associated with the 
data itself can be valuable information on the task of identifying
entities. Yet, we cannot expect these features to be completely constrained 
by an underlying pattern. Organization patterns tend to follow some guidelines 
but they are in no way subject to strict rules. That is why classical web data 
extraction systems such as automatic wrapper generators 
\cite{Kushmerick2000,Hsu1998,Muslea1999}
do not translate very well across different websites.

Most existing Web data extraction methods are tailored to extract data 
from a single Web page, producing different compromises between efficacy and 
degree of human supervision. Some unsupervised approaches proposed to tackle 
the problem of data extraction for whole application domains 
\cite{Zhu2005,Zhu2006,Abdessalem2010,Furche2012,Furche2012a}. Usually, 
unsupervised WDE methods work in two stages. In the record segmentation stage,
WDE systems seek to cluster visually and structurally similar web page regions 
and identify repeating data records, usually with heuristics and 
hand-coded rules. In the attribute labelling stage, WDE systems seek to identify 
the correct attributes on data records, many times resorting to regular expressions 
or gazetteer matching strategies. The outcome of each of these stages can aid one 
another. The inner patterns of data records can help identifying attributes in other 
data records. Also, by properly identifying data record attributes, it becomes 
easier to determine boundaries and perform record segmentation.

While unsupervised approaches can be sometimes adequate to extract information from 
webpages with similar templates, they usually fail on cross-website data extraction 
tasks. Also, more sophisticated approaches may be needed when we are not dealing
with easily distinguishable attributes such as prices and dates. In this regard, 
machine-learning-based sequence labeling methods can provide a more flexible 
approach that works regardless of website structure.

In recent years, we saw an amazing progress in the field of Natural Language Processing, 
particularly with the introduction of deep recurrent neural network architectures
for sequence labeling. However, despite web data extraction being a closely 
related field, there is a lack of extraction tools that make use of these recent 
advancements. The attribute labelling stage in web data extraction systems
is essentialy a Named Entity Recognition (NER) problem, the problem of 
detecting named entities in the text and classifying them into predetermined 
categories such as person names, locations, dates or organizations.

In many cases, such as when we are extracting researcher names from faculty listings,
detecting named entities is sufficient to solve the data extraction task. However, when we are
dealing with multi attribute data records or complex relationships, we may need to 
perform additional steps. Nevertheless, even in the latter cases, flexible NER methods 
are still desirable because, while many WDE algorithms can effectively exploit the 
semi-structured nature of web documents, too much reliance on structural webpage 
features often produce poor generalizations on cross website extraction. Also, 
data records may enclose plain text with relevant named entities.

In this paper, we investigate methods of named entity recognition for web data extraction.
Recently proposed neural architectures have achieved exciting results 
on the NER task in plain text while requiring almost 
no feature engineering or access to gazetteers \cite{Huang2015,Lample2016,Ma2016}. 
NER on HTML poses a slightly different type of challenge. Named entities may occur inside 
tables, lists, graphs or other types of visual elements that provide little to no textual 
information that could give hints about the semantic category of a word. Still, even 
with this limitation, we show that it is possible to obtain very good results with a 
relatively small training set.

By reliably detecting named entities on HTML, we can improve the performance of existing WDE 
approaches or even construct an end-to-end neural network architecture to tackle domain 
wide extraction with considerable flexibility. To test different NER approaches to
web data extraction, we explored the task of researcher name extraction from university 
faculty listings across the world, introducing a novel NER dataset.

Reliable researcher affiliation information is often missing from public researcher 
databases (especially in departments other than Computer Science). Also, the display of 
faculty information varies significantly between different university websites, so 
this task can provide a good measure of the expected performance and data need of
NER methods on other web data extraction tasks.

\section{Related Work}

In the last 20 years, the astonishing growth of public information in the web has 
led to the development of a number of different approaches to the problem of web 
data extraction. Traditionally, the task was solved by designing special purpose
programs called wrappers to recognize relevant data and store records in a structured
format. These early tools varied wildly relative to their degree of automation.

It was readily perceived that manual wrapper generation was a rather tedious and
error prone process, unsuited for large scale operations. Wrappers tend to
break frequently because they rely heavily on web page features that can change 
often. So, in the late nineties, several authors advocated for wrapper induction, a technique 
that consists of automatically constructing wrappers from a small set of examples by 
identifying delimiters or context tokens that single out the desired attributes. 
Some remarkable wrapper induction methods are WIEN \cite{Kushmerick2000}, Soft 
Mealy \cite{Hsu1998} and STALKER \cite{Muslea1999}.

@@

Other approaches such as NoDoSE \cite{Adelberg1998} and Debye \cite{Laender2002a} 
brought greater flexibility to wrapper induction methods by requiring a greater level 
of human interaction through graphical user interfaces. Web data extraction techniques often 
require some sort of assistance from human experts to boost accuracy. One of the main challenges 
in the field lies in determining an adequate tradeoff between the degree of automation and 
the precision and recall of the data extraction tool.

To automate the task of web data extraction completely some approaches,
such as Road Runner \cite{Crescenzi2001}, removed entirely the need for data examples.
Road Runner parses documents belonging to a same class (e.g. books on Amazon) and 
generates wrappers based on their similarities and differences, yielding comparable results 
to those obtained by wrapper induction methods. However, like previous approaches, it was 
unsuited for cross site extraction tasks because the learned rules were not general enough.

NLP based approaches aimed at extracting more general rules that could possibly
be employed over multiple websites. RAPIER \cite{Califf1999} is a method of rule
extraction that uses information such as part-of-speech tags and semantic classes from
a lexicon to derive patterns from a set of training examples. This approach is more
flexible than the wrapper induction methods, however it achieves much lower rates of 
recall and precision.

In 2002, a survey by Laender et al. \cite{Laender2002} made a thorough classification of the
early approaches with a taxonomy based on their main technology, being them: languages for
wrapper development, HTML-aware tools, NLP-based tools, Wrapper Induction Tools,
Modeling-based tools and Ontology-based tools. Some noteworthy examples from this era
are:

\begin{itemize}
\item TSIMMIS \cite{Hammer1997} and WebOQL \cite{Arocena1999}, which are special purpose 
languages for building wrappers.

\item Road Runner \cite{Crescenzi2001}, XWRAP \cite{Liu2000} and W4F \cite{Sahuguet1999}, 
which are HTML-aware tools that infer meaningful patterns from the HTML structure.

\item RAPIER \cite{Califf1999}, SRV \cite{Freitag1998}, WHISK \cite{Soderland1999}, which 
are NLP-based tools.

\item WIEN \cite{Kushmerick2000}, Soft Mealy \cite{Hsu1998} and STALKER \cite{Muslea1999} which 
are wrapper induction methods.

\item NoDoSE \cite{Adelberg1998} and Debye \cite{Laender2002a}, which are semi supervised modeling
based tools that require some interaction with the user by means of a graphical
user interface.
\end{itemize}

In 2006, Chang et al. \cite{Chang2006} complemented the previous surveys with semisupervised 
technologies such as Thresher \cite{Hogue2005}, IEPAD \cite{Chang2001} and 
OLERA \cite{Chang2004}. They differed from supervised 
and unsupervised methods because they either needed only a rough description of
data from users for extraction rule generation or some level of post processing
that needed user attention. The survey also mentioned newer unsupervised methods
such as DeLa \cite{Wang2003}, Exalg \cite{Arasu2003} and Depta \cite{Zhai2005}.

Most of the early information extraction systems were rule-based with either 
manual rule description or automatic rule learning from examples, thus they
suffered from a lack of flexibility when dealing with noisy and unstructured data.
Huge progress in the field of statistical learning led to the development of
statistical models that tried to solve this problem.

In 2008, Sarawagi \cite{Sarawagi2008} produced a survey that classified wrappers into
rule-based methods, statistical methods and hybrid models, bringing together 
the fields of named entity recognition, relationship extraction and information extraction. 
The rule based methods encompass most of the 
previous models. The statistical methods convert the extraction task into a token labeling 
task, identifying the target entities through the assignment of labels as in a typical 
Named Entity Recognition task. Traditionally, Hidden Markov Models \cite{Leek1997,Freitag1999}, 
Linear Chain Conditional Random Fields \cite{Lafferty2001}, and Maximum Entropy Taggers 
\cite{McCallum2000} have been the usual choice for linear sequence tagging models.
More recently, with the advancement of Natural Language Processing and Deep Learning, 
neural models outperformed previous NER methods for plain text. Huang et. al. \cite{Huang2015} introduced the 
bidirectional Long Short-Term Memory (LSTM) model with a Conditional Random Field (CRF) output layer
for NER. Ma and Hovy \cite{Ma2016} incorporated Convolutional Neural Network based character representations 
on top of the architecture. And Lample et. al. \cite{Lample2016} introduced
LSTM based character representations.

Surveys by Ferrara et al. \cite{Ferrara2014}, Schulz et al. \cite{Schulz2016} and 
Varlamov et al. \cite{Varlamov2016} updated the previous surveys on information 
extraction methods with some interesting innovations. 
Some examples are: the Visual Box Model \cite{Krupl2005}, a data extraction system that produces 
a visualization of the web page to exploit visual cues to identify data presented in a tabular form;
automatic wrapper adaptation \cite{Ferrara2011}, a technique that tries to reduce the cost of 
wrapper maintenance by measuring the similarity of HTML trees and adapting
wrappers to the new page structure; AutoRM \cite{Shi2015}, a method to mine
records from a single web page by identifying similar data regions through DOM
tree analysis; Knowledge Vault \cite{Dong2014}, a method that combines different 
extraction approaches to feed a probabilistic knowledge base.

Most data extraction systems focus on extracting information from single websites
and are therefore unsuited for cross website extraction tasks. Even unsupervised
approaches that are domain independent, such as RoadRunner \cite{Crescenzi2001} 
and EXALG \cite{Arasu2003} only work well for extracting data from pages generated 
from a same template.

A statistical approach to unsupervised domain 
independent web data extraction was described by Zhu et al \cite{Zhu2005}. The 2D CRF 
model takes a web page segmented into data blocks and employs a two dimensional conditional 
random field model to perform attribute labelling. The model was further improved
\cite{Zhu2006} to model record segmentation and attribute labelling as a joint task.
Some of the limitations of early unsupervised methods 
were also tackled by ObjectRunner \cite{Abdessalem2010} and AMBER \cite{Furche2012}. 
These methods work by annotating webpages automatically with regular expressions, gazetteers and 
knowledge bases. They can rectify low quality annotations and even improve the annotators
by exploring regular structures in the DOM during the record segmentation phase.

Web data extraction methods have undoubtedly improved extraordinarily, but
as pointed by Schulz et al. \cite{Schulz2016}, it is difficult to compare the results 
achieved by competing tools, and many seem to rely excessively on heuristic methods.
In that regard, the recent advancements in sequence taggers may provide more robust and
flexible extraction tools.

@@

HMM based taggers have been succesfully applied in many NLP and WDE tasks 
\cite{Rabiner1990,Leek1997,Freitag2000}. They are incredibly fast to train and also they are very 
interpretable, making them a good choice for a first approximation. However, these models 
are highly dependent on the right selection of features, what may outweigh the benefit of a 
small training cost.

>>>>

\usepackage{booktabs} % For formal tables
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{amsfonts}
\usepackage{multirow}
\usepackage{glossaries}
\usepackage{tikz}
\usepackage{pgfplots}

@@

\makeglossaries
\newacronym{nlp}{NLP}{Natural Language Processing}
\newacronym{wde}{WDE}{Web Data Extraction}
\newacronym{ner}{NER}{Named Entity Recognition}
\newacronym{hmm}{HMM}{Hidden Markov Models}
\newacronym{crf}{CRF}{Conditional Random Fields}
\newacronym{lstm}{LSTM}{Long Short-Term Memory Networks}
\newacronym{ie}{IE}{Information Extraction}
\newacronym{rne}{RNE}{Researcher Name Extraction}
\newacronym{rnn}{RNN}{Recurrent Neural Networks}
\newacronym{cnn}{CNN}{Convolutional Neural Networks}
\newacronym{pos}{POS}{Part-of-Speech}

@@

\title{Named Entity Recognition for Web Data Extraction}

% \author[João Mateus de Freitas Veneroso and Berthier Ribeiro-Neto]
%        {João Mateus de Freitas Veneroso$^A$ \and
%         Berthier Ribeiro-Neto$^B$\\
% 	Universidade Federal de Minas Gerais$^{A,B}$ \\
% 	Google Engineering$^A$, Belo Horizonte - MG, Brazil}

% \affiliation{%
%   \institution{Universidade Federal de Minas Gerais}
%   \streetaddress{Av. Pres. Antônio Carlos, 6627 - Pampulha}
%   \city{Belo Horizonte}
%   \state{MG}
%   \postcode{31270-901}
%   \country{Brazil}}
% \email{jmfveneroso@gmail.com}
% 
% \author{Berthier Ribeiro-Neto}
% \affiliation{%
%   \institution{Universidade Federal de Minas Gerais}
%   \streetaddress{Av. Pres. Antônio Carlos, 6627 - Pampulha}
%   \city{Belo Horizonte}
%   \state{MG}
%   \postcode{31270-901}
%   \country{Brazil}}
% \email{berthier@dcc.ufmg.br}
% \email{berthier@google.com}

@@

% \gls{wde} methods often rely on hand-coded rules to 
% identify and extract data from webpages. These methods are usually
% suited for extracting information from pages within
% the same website, however they perform poorly on extraction 
% tasks across different websites. Alternatively, statistical and 
% machine-learning-based sequence labeling methods provide a more flexible 
% approach to Web data extraction. Many times, HTML pages are very different 
% from plain text, because sentences are too short to provide adequate 
% context for conventional Named Entity Recognition methods to work 
% properly. Also, the HTML structure may encode information that is not 
% replicated in the text. Nonetheless, these limitations can be overcome by
% adequate feature engineering, the use of pretrained word 
% embeddings and neural character representations. In this article, we 
% evaluate the performance of different methods of named entity recognition 
% on the task of Web data extraction. In particular, we introduce a novel 
% dataset\footnote{The dataset and all models discussed in this article are 
% available in: https://github.com/jmfveneroso/ner-on-html.} 
% consisting of faculty listings from university webpages across
% the world in multiple languages and test the NER models on the task of 
% extracting researcher names from these listings. We found that a 
% neural network architecture that combines a bidirectional LSTM with
% a Conditional Random Fields output layer and LSTM-based character 
% representations outperforms other methods on the researcher name 
% extraction task, achieving an F1-score of 0.8867 with no feature engineering. 
% With the addition of hand crafted features, the F1-score can be slightly 
% improved to 0.8995.

Web Data Extraction methods often rely on hand-coded rules to 
identify and extract data from webpages. These methods are
suited for extracting information from pages within
the same website, however they perform poorly on extraction 
tasks across different websites. Alternatively, 
machine-learning-based Named Entity Recognition methods provide a more flexible 
approach to Web Data Extraction. However, many times webpages are very different 
from plain text, because sentences are too short to provide adequate 
context for conventional Named Entity Recognition models to work 
properly. 
% Nonetheless, the HTML structure also encodes useful information that 
% can be used by NER models to achieve a better performance. We propose a
% method to use this information: the self-training strategy for Hidden Markov
% Models.
In this article, we 
evaluate the performance of different methods of Named Entity Recognition
in the task of Web Data Extraction. In particular, we introduce a novel 
dataset consisting of faculty listings from university webpages across
the world in multiple languages and test different Named Entity Recognition 
models in the task of 
extracting researcher names from these listings. We found that a 
neural network architecture that combines a bidirectional LSTM with
a Conditional Random Fields output layer and LSTM-based character 
representations outperforms other methods achieving 90.2 F1 in 
the task. However, with the self-training strategy, we can get a much simpler 
model, the second-order Hidden Markov Model, to achieve 87.9 F1.

@@

@@

\gls{wde} is the task of automatically extracting structured 
information from unstructured or semi-structured web documents. The input 
usually consists of web documents containing a number of predetermined entities 
organized in a similar manner. The \gls{wde} task consists of 
identifying these entities and organizing them according to a template.

HTML documents most often lie in between the structured/unstructured 
data paradigm. DOM hierarchy, element disposition, CSS classes, and other 
features related to the document structure and indirectly associated with the 
data itself can be valuable information on the task of identifying
entities. Yet, we cannot expect these features to be completely constrained 
by an underlying pattern. Organization patterns tend to follow some guidelines 
but they are in no way subject to strict rules. That is why classical \gls{wde} 
systems such as automatic wrapper generators 
\cite{Kushmerick2000,Hsu1998,Muslea1999}
do not translate very well across different websites.

Most existing \gls{wde} methods are tailored to extract data 
from a single webpage, producing different compromises between efficacy and 
degree of human supervision. Some unsupervised approaches proposed to tackle 
the problem of data extraction for whole application domains 
\cite{Crescenzi2001}. Usually, 
unsupervised \gls{wde} methods work in two stages. In the record segmentation stage,
WDE systems seek to cluster visually and structurally similar webpage regions 
and identify repeating data records with heuristics and 
hand-coded rules. In the attribute labeling stage, WDE systems seek to identify 
the correct attributes on data records, many times resorting to regular expressions 
or gazetteer matching strategies. The outcome of each of these stages can aid one 
another. The inner patterns of data records can help in identifying attributes of other 
data records. Also, by properly identifying data record attributes, it becomes 
easier to determine boundaries and perform record segmentation.

While unsupervised approaches can be sometimes adequate to extract information from 
webpages with similar templates, they usually fail on cross-website data extraction 
tasks. Also, more sophisticated approaches may be needed when we are not dealing
with easily distinguishable attributes such as prices and dates. 
Comparatively, statistical machine learning provides more robust and flexible methods
of \gls{wde}. In recent years, we saw amazing progress in 
the field of \gls{nlp} that is extremely relevant to
the \gls{wde} community, particularly with the introduction of Deep Neural Networks 
for Sequence Labeling~\cite{Collobert2011}, but these advancements were 
not widely incorporated by \gls{wde} systems. Also, most of the attention of the \gls{nlp} community 
regarding this topic is devoted to solving \gls{ie} tasks in plain text, such as 
the identification of people and organizations in news texts.
However, the difference between some types of webpages and plain text is significant, so
\gls{ie} systems trained in plain text datasets tend to perform poorly 
when confronted with some web extraction tasks, as we have confirmed in our experiments.

A concrete example of a \gls{wde} problem that demands the type of
flexible solution provided by statistical machine learning methods is the extraction of 
researcher names from faculty directories. Automatically extracting researcher information 
from university websites is important, for example, to construct researcher affiliation databases 
and compare the academic impact of research groups using bibliographic indices~\cite{Ribas2015}. 
The problem of \gls{rne} can be solved with machine learning methods of 
\gls{ner}.

Many \gls{wde} tasks in the web share a common
factor with the \gls{rne} task. That is, they need to extract similar
entities from different webpages or they need to extract entities from short snippets of text 
instead of complete sentences. Some examples would be comment extraction from blog
posts and \gls{ner} in tweets. Because of the lack of context in tweets, \gls{ner} methods trained 
in conventional plain text corpora tend to perform badly for more or less the same reasons 
they perform badly in other \gls{wde} tasks.

In this article, we compare different machine learning approaches to 
\gls{ner} on the web by evaluating their performance in the 
\gls{rne} task. With this purpose in mind, we introduce a novel \gls{ner} dataset 
with labeled entities, consisting of faculty directories from universities across the world. 
We compare the models in terms of their Precision, Recall, F-scores and their 
overall complexity. That is, even if a model has a slightly worse performance in terms of the
objective evaluation metrics in comparison to other approaches, it may still be useful if it 
is considerably simpler and faster to train.
The tested models were the \gls{hmm} up to third order, \gls{crf}, and a range of Deep Learning 
architectures based on Bidirectional \gls{lstm}. We also 
introduce the self-training strategy that can boost the performance 
of \gls{hmm}s in sequence labeling tasks for the web.

The usability of the evaluated models is not limited to the particular problem of \gls{rne}. 
By reliably detecting named entities on the web, we can boost the performance 
of existing \gls{wde} approaches or even construct an end-to-end architecture that
solves the problem of data extraction across different websites with improved robustness. Also, 
the researcher affiliation database constructed with the application of these methods will
be made public in the future to provide deeper insight in bibliometric studies about the
scientific impact of research groups.

\section{Related Work}
\label{cha:related_work}

The \gls{rne} task is a problem in \gls{wde} that
we proposed to solve with the application of machine learning methods of \gls{ner}.
This chapter presents the related research in the fields of \gls{wde} 
in Section~\ref{sec:wde} and \gls{ner} in Section~\ref{sec:ner}.

\subsection{Web Data Extraction}
\label{sec:wde}

Since the early 1990s, the astonishing growth of public information in the web has 
led to the development of a number of different approaches to the problem of \gls{wde}.
Traditionally, the task was solved by designing special purpose
programs called wrappers to recognize relevant data and store records in a structured
format. These early tools varied wildly relative to their degree of automation.

It was readily perceived that manual wrapper generation was a rather tedious and
error prone process, unsuited for large scale operations. Wrappers tend to
break frequently because they rely on webpage features that can change 
often. So, in the late nineties, several authors advocated for wrapper induction, a technique 
that consists of automatically constructing wrappers from a small set of examples by 
identifying delimiters or context tokens that single out the desired attributes. 
Some remarkable wrapper induction methods are WIEN~\cite{Kushmerick2000}, Soft 
Mealy~\cite{Hsu1998} and STALKER~\cite{Muslea1999}.

@@

Other approaches such as NoDoSE~\cite{Adelberg1998} and Debye~\cite{Laender2002a} 
brought greater flexibility to wrapper induction methods by requiring a greater level 
of human interaction through graphical user interfaces. \gls{wde} techniques often 
require some sort of assistance from human experts to boost accuracy. One of the main challenges 
in the field lies in determining an adequate trade-off between the degree of automation and 
the Precision and Recall of the data extraction tool.

To automate the task of \gls{wde} completely some approaches,
such as Road Runner~\cite{Crescenzi2001}, removed entirely the need for data examples.
Road Runner parses documents belonging to a same class (e.g. books in Amazon) and 
generates wrappers based on their similarities and differences, yielding comparable results 
to those obtained by wrapper induction methods. However, like previous approaches, it was 
unsuited for cross site extraction tasks because the learned rules were not general enough.

Early NLP-based approaches aimed at extracting more general rules that could possibly
be employed over multiple websites. RAPIER~\cite{Califf1999} is a method of rule
extraction that uses information such as part-of-speech tags and semantic classes from
a lexicon to derive patterns from a set of training examples. This approach is more
flexible than the wrapper induction methods, however it achieves much lower rates of 
Precision and Recall.

A survey by Laender, Ribeiro-Neto, da Silva and Teixeira~\shortcite{Laender2002b} made a thorough classification of the
early approaches with a taxonomy based on their main technology, being them: languages for
wrapper development, HTML-aware tools, NLP-based tools, Wrapper Induction Tools,
Modeling-based tools and Ontology-based tools. Some noteworthy examples from this era
are: 
%
\begin{itemize}
\item TSIMMIS~\cite{Hammer1997} and WebOQL~\cite{Arocena1999}, which are special purpose 
languages for building wrappers.
\item Road Runner~\cite{Crescenzi2001}, XWRAP~\cite{Liu2000} and W4F~\cite{Sahuguet1999}, 
which are HTML-aware tools that infer meaningful patterns from the HTML structure.
\item RAPIER~\cite{Califf1999}, SRV~\cite{Freitag1998}, WHISK~\cite{Soderland1999}, which 
are NLP-based tools.
\item WIEN~\cite{Kushmerick2000}, Soft Mealy~\cite{Hsu1998} and STALKER~\cite{Muslea1999} which 
are wrapper induction methods.
\item NoDoSE~\cite{Adelberg1998} and Debye~\cite{Laender2002a}, which are semi-supervised
tools that require some interaction with the user by means of a graphical
user interface.
\end{itemize}
%
% Text Runner.
% https://www.aaai.org/Papers/IJCAI/2007/IJCAI07-429.pdf
\cite{Chang2006} complemented the previous surveys with semi-supervised 
technologies such as Thresher~\cite{Hogue2005}, IEPAD~\cite{Chang2001} and 
OLERA~\cite{Chang2004}. They differed from supervised 
and unsupervised methods because they either needed only a rough description of
data from users for extraction rule generation or some level of post processing
that needed user attention. 
%The survey also mentioned newer unsupervised methods
% such as DeLa~\cite{Wang2003}, Exalg~\cite{Arasu2003} and Depta~\cite{Zhai2005}.

Most of the early \gls{wde} systems were rule-based with either 
manual rule description or automatic rule learning from examples, thus they
suffered from a lack of flexibility when dealing with noisy and unstructured data.
Huge progress in the field of statistical learning led to the development of
models that tried to solve this problem.

\cite{Sarawagi2008} introduced a classification that segmented wrappers in
rule-based methods, statistical methods and hybrid models, bringing together 
the fields of \gls{ner}, Relationship Extraction and \gls{wde}. 
The rule based methods encompass most of the previous models. While the statistical methods 
convert the extraction task into a token labeling task, solved with \gls{ner} 
and Relationship Extractions methods. Traditionally, these subtasks were solved with 
generative models based on \gls{hmm}s or discriminative models based on the 
Maximum Entropy principle, but recently these have been largely superseded by Deep Neural 
Networks. Different from automatic wrapper generators, statistical methods are suitable for
a large variety of tasks, especially when we want the system to handle cross website information 
extraction and plain text information extraction. That is why this class of methods is of 
special interest to our application. The progress of statistical models will be 
discussed in Section~\ref{sec:ner}.

Surveys by~\cite{Ferrara2014}, \cite{Schulz2016} and \cite{Varlamov2016} updated the 
previous surveys on Information Extraction methods with some interesting innovations. 
Some examples are: the Visual Box Model~\cite{Krupl2005}, a data extraction system that produces 
a visualization of the webpage to exploit visual cues to identify records presented in a tabular form;
automatic wrapper adaptation~\cite{Ferrara2011}, a technique that tries to reduce the cost of 
wrapper maintenance by measuring the similarity of HTML trees and adapting
wrappers to the new page structure; AutoRM~\cite{Shi2015}, a method to mine
records from a single webpage by identifying similar data regions through DOM
tree analysis; and Knowledge Vault~\cite{Dong2014}, a method that combines different 
extraction approaches to feed a probabilistic knowledge base.

Most data extraction systems focus on extracting information from single websites
and are therefore unsuited for cross website extraction tasks. Even unsupervised
approaches that are application domain independent, such as RoadRunner and EXALG, 
only work well when extracting data from pages generated from a same template.

A statistical approach to unsupervised domain 
independent \gls{wde} was described by~\cite{Zhu2005}. The 2D CRF 
model takes a webpage segmented into data blocks and employs a two dimensional \gls{crf}
model to perform attribute labeling. The model was further improved 
in~\cite{Zhu2006} to model record segmentation and attribute labeling as a joint task.
Some of the limitations of early unsupervised methods 
were also addressed by ObjectRunner~\cite{Abdessalem2010} and DIADEM~\cite{Furche2012}. 
These methods work by annotating webpages automatically with regular expressions, gazetteers and 
knowledge bases. They can rectify low quality annotations and even improve the annotators
by exploring regular structures in the DOM during the record segmentation phase.

\gls{wde} methods have undoubtedly improved extraordinarily, but
as pointed by \cite{Schulz2016}, it is difficult to compare the results 
achieved by competing tools. Also, many tools seem to rely excessively on heuristic methods.
The recent advancements in sequence taggers may provide more robust and flexible techniques
to address this problem.

\subsection{Named Entity Recognition}
\label{sec:ner}

\gls{ner} is an important subtask in \gls{ie}.
The \gls{ner} task was defined in the Third Message 
Understanding Conference (MUC-3)~\cite{Sundheim1991}, where researchers were asked to extract
entities from a news corpus about terrorist incidents. However, it was the 
language-independent \gls{ner} shared task at the Conference 
on Computational Natural Language Learning in 2003 ({CoNLL-2003})~\cite{KimSang2003},
that established an enduring labeled dataset constructed with news texts from Reuters.
Despite its reduced size and the limited variability of its documents, the {CoNLL-2003}
dataset is still used to compare the performance of NER systems in English and 
German.

Sequence labeling for \gls{ner} and \gls{pos} tagging (labeling nouns, verbs, pronouns, etc.) 
is very similar, so, many times, research articles that propose new methods for \gls{ner}
also report results for the \gls{pos} Tagging task. And frequently, the best methods for 
\gls{pos} Tagging are also the best methods for \gls{ner}.

Traditionally, the \gls{ner} task was solved with generative models based on 
\gls{hmm}s. The first appearance of \gls{hmm}s in the
field of \gls{nlp} occurred in the mid-seventies and was
primarily focused on the problem of Speech Recognition. 
But in the late nineties, \gls{hmm}s also found important applications in \gls{ie}
and \gls{ner} as in the works by~\cite{Bikel1999}, 
\cite{Freitag1999}, and \cite{Freitag2000}.

The problem with \gls{hmm}s is that they model the joint probability between 
sequences of observations and labels $ P(X, Y) $, a harder problem than modelling the corresponding 
conditional probability $ P(Y|X) $. They assume conditional independence for the observations $ X $, and
therefore, they cannot handle overlapping features. This lack of flexibility led to the 
development of discriminative approaches to sequence labeling based on the Maximum Entropy principle.

Some early examples are Maximum Entropy Taggers for NER~\cite{Borthwick1998} and
\gls{pos} Tagging~\cite{Ratnaparkhi1998}. The Maximum Entropy Markov Model~\cite{McCallum2000} 
was developed just a while later, building up on the intuition of \gls{hmm}s combined with
the flexibility of discriminative approaches. However, because of the label bias problem,
this model was superseded by \gls{crf}s~\cite{Lafferty2001, McCallum2003}. 
At this time, the best performing systems almost always resorted to external gazetteers 
and hand-chosen features, as is the case for the {CoNLL-2003} winning model~\cite{Florian2003}.

With the advancement of Machine Learning in recent years, we saw the rise
of Neural Networks applied to sequence labeling. In 2011, \cite{Collobert2011} 
introduced Neural Networks free of feature engineering to sequence labeling tasks,
using \gls{cnn} over word embeddings with a CRF output layer to tackle 
the problems of \gls{pos} tagging, Chunking, Semantic Role Labeling, and NER. A similar architecture 
proposed in 2015 by~\cite{Huang2015}, the Bi-LSTM-CRF, replaced the \gls{cnn} in \cite{Collobert2011} 
with a bidirectional LSTM, achieving better results.

In 2016, further advancement to the NER models was achieved by incorporating character 
representations at the bottom of the Bi-LSTM-CRF architecture to extract morphological 
features from words automatically. The model by~\cite{Lample2016} uses a 
bidirectional \gls{lstm} over character embeddings and the model by~\cite{Ma2016} uses a
one dimensional \gls{cnn} with max pooling over character embeddings. Both models also 
made use of pre-trained GloVe word embeddings, created by~\cite{Pennington2014}.

Small improvements to NER systems have been made since then, primarily due to the 
introduction of new word embeddings on variations of the Bi-LSTM-CRF architecture. From
this group, we can mention ELMo~\cite{Peters2018}, BERT~\cite{Devlin2018}, and
Flair~\cite{Akbik2018}. 
All of them were introduced in 2018 and they differ primarily 
in how to construct contextual embeddings from the internal states of a language 
modelling neural network.

To our knowledge, the best NER system up to this date (considering the performance in the
{CoNLL-2003} dataset) is the bidirectional transformer model proposed by~\cite{Baevski2019} that uses
a stack of self-attention modules and ELMo embeddings. Table~\ref{tab:ner_model_comparison}
shows a comparison of the history of reported F1 scores in the English test set of the {CoNLL-2003} dataset
for the NER systems that were mentioned in this section. Each of the mentioned systems held the 
record for the task at a given time.

\begin{table}[h]
  \small
  \begin{center}
    \begin{tabular}{ lc }
      \toprule
      Model & Test F1 \\
      \midrule
       \cite{Florian2003} ({CoNLL-2003} Winner)    & 88.76 \\
       \cite{Collobert2011}                        & 89.59 \\
       \cite{Huang2015}                            & 90.10 \\
       \cite{Lample2016}                           & 90.94 \\
       \cite{Ma2016}                               & 91.21 \\
       \cite{Peters2018}                           & 92.22 \\
       \cite{Devlin2018}                           & 92.80 \\
       \cite{Akbik2018}                            & 93.09 \\
       \cite{Baevski2019}                          & 93.50 \\
      \bottomrule
    \end{tabular}
  \end{center}
  \caption{Model performances in the {CoNLL-2003} English test set.}
  \label{tab:ner_model_comparison}
\end{table}

@@

HMM based taggers have been successfully applied in many NLP and WDE tasks 
\cite{Rabiner1990,Freitag2000}. They are incredibly fast to train and also they are very 
interpretable, making them a good choice for a first approximation. However, these models 
are highly dependent on the right selection of features, what may outweigh the benefit of a 
small training cost.
